Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-23 article/article.tex
Commit 2024-05-23 19:10

\caption{Statistics of the number of CE occurancies for each month. The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies}
\end{figure}

@@

\ldots{} \citet{Zhang2018} \ldots.

@@

\caption{Relation of mean over irradiance and CE group duration}\label{fig:unnamed-chunk-3}
\end{figure}

@@

Another aspect of the CE events are the cases when the irradiance is
above the expected irradiance on top of the atmosphere, we have defined
this as ECE (Equation\nobreakspace{}\ref{eq:ECE}).

@@

Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies}
we have computed the distribution of the number of occurrences of ECE
events by month in
Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the
most active period is in the spring (March -- May), followed by the
months of June, September and October.

@@

\caption{Distribution of }\label{fig:relative-month-occurancies-ECE}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-4}
\end{figure}

>>>>

\caption{Seasonal statistics of the number of CE occurancies for each month, normalized to the maximum occurancies on June. The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies}
\end{figure}

@@

The relation between the duration and the mean OIR intensity of the
groups have been studied (Figure\nobreakspace{}\ref{fig:group-2d}). We
observe that the GCE events tend to have either long duration, or large
intensity, events with strong enhancement and long duration are very
rare. A similar result on this relation, have been also reported by
\citet{Zhang2018}, on a study using a far higher sampling rate than
ours.

@@

\caption{Relation of mean over irradiance and CE group duration}\label{fig:group-2d}
\end{figure}

@@

A characteristic of the CE events that is commonly reported and has some
significance on the solar energy production infrastructure are the
extreme CE events (ECE). Where solar irradiance exceeds the expected
irradiance on top of the atmosphere, we have defined this as ECE
(Equation\nobreakspace{}\ref{eq:ECE}).

@@

Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies}
we have computed the distribution of the number of occurrences of ECE
events by month in
Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the
most active period is in the spring and the start of the summer (March
-- June), followed by the late fall (Septemcer and October).

@@

\caption{Seasonal statistics of the number of ECE occurancies for each month, normalized to the maximum occurancies on March. The box represents the values of the low $25\,\%$ percentile to $75\,\%$ percentile, where the thick horizontal line inside is the mean, the verical lines extend to the macimum and minimum vales, the dots are outlier values, and the rhombus is the mean.}\label{fig:relative-month-occurancies-ECE}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-3}
\end{figure}
